%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Key Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


    %---------------------------------------------------------
    \cventry
    {Lead Platform Engineer} % Job title
    {Gotrade Pte Ltd} % Organization
    {Singapore} % Location
    {May. 2022 - Present} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimized infrastructure design, saving over 70\% in monthly cost (100K) and enabling scalable growth.}
        \item {Accelerated CI/CD by more than 99\% through custom P2P nix-based runners.}
        \item {Led successful migration to Kubernetes on EKS, improving platform agility and reducing operational overhead.}
        \item {Standardized development workflow with nix-first environments, boosting team productivity and code reusability.}
        \item {Increased system availability to 99.9\% through implementing comprehensive Observability practices with LGTM Stack and OpenTelemetry.}
        \item {Setup on-call systems, metrics and alarms with routing rules to correctly notify engineers.}
        \item {Architected high-performance internal ledger for high-volume trades, enabling efficient transaction processing using Kafka.}
        \item {Evangelized IaC, containerization, and automated testing through weekly "MasterClasses," fostering a culture of innovation.}
    \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Site Reliability Engineer} % Job title
    {ByteDance} % Organization
    {Singapore} % Location
    {Jan. 2021 - Dec 2021} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyse, resolve and regress alarms for TikTok's Live-Streaming CDN}
        \item {Designed and deployed stack platform to manage multi-region multi-language multi-timezone on-call rostering}
        \item {Developed a distributed and stateless bot framework that reduced time taken to create a new bot by up to 98.5\%}
        \item {Leveraging on self-written framework to design platform to automate playbooks}
        \item {Push and present benefits of Nix as a envrionment management tool}
        \item {Obtain sales lead for Lark product}
    \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Backend Engineer} % Job title
    {Innosparks, ST Engineering} % Organization
    {Singapore} % Location
    {Jul. 2018 - Jul. 2019} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built healthcare platform for post-acute care for Singapore's Ministry of Health }
        \item {Led team to implement RESTful API server in .NET Core in C\# }
        \item {Setup authentication integration with Auth0 as Identity service}
        \item {Provisioned manageable infrastructure with on Azure with Azure ActiveDirectory}
        \item {Deployed centralised monitoring environment (Application Insights) which gathers system and run-time metrics from Azure resource nodes}
        \item {Built fully automated CI/CD pipelines on AzureDevops with Azure and Docker}
        \item {Automated load tests in staging environment for performance testing}
        \item {Devised a computer vision algorithm to extract a patient's particulars from the National Registration Identity Card}
        \item {Built prototype of frontend project in React.js}
    \end{cvitems}
    }

   
\end{cventries}
